Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-06-01 Paper/gammaRays.tex
Updated the paper with 256 bursts sample
Updated paper with 4096 points sample

\begin{figure}
	\centering
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{sampleLightCurveLogNegative}
		\label{fig:sampleLightCurveLogNegative}
		\caption{Stretching factor $\kappa = 0.868$, redshift $z = 0.934$, off-axis angle $\chi = 4.65\times 10^{-4}$.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{sampleLightCurveLogPositive}
		\label{fig:sampleLightCurveLogPosivie}
		\caption{Stretching factor $\kappa = 5.33$, redshift $z = 0.229$, off-axis angle $\chi = 8.97\times 10^{-3}$.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{\the\linewidth
		High and low energy light curves produced by the geometrical model. Burst parameter values are the same as discussed in section \ref{sec:parameters}.
	}
	\label{fig:sampleLightCurves}
\end{figure}

@@

\begin{figure}
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionHistogram}
		\label{fig:kappaDistributionHistogram}
		\caption{Histogram (blue) obtained from the model. Bar lines (black) show observed stretching factors.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionCDF}
		\label{fig:kappaDistributionCDF}
		\caption{CDF (blue) obtained from the model. Gray curve and bar lines show observed stretching factors.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{Stretching factors histogram and CDF produced by our model. The sample contains $16$ bursts.}
	\label{fig:kappaDistribution}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{correlations}
        \caption{Correlations between off-axis angles, stretching factors and high to low energy photon count ratios found in the sample produces by our model. The sample contains $16$ bursts. Black crosses show observations. This correlation allows to estimate off-axis angles of observed bursts.}
        \label{fig:correlations}
\end{figure}

>>>>

\begin{figure}
	\centering
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{sampleLightCurveLogNegative}
		\label{fig:sampleLightCurveLogNegative}
		\caption{Stretching factor $\kappa = 0.821$, redshift $z = 1.82$, off-axis angle $\chi = 0$.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{sampleLightCurveLogPositive}
		\label{fig:sampleLightCurveLogPosivie}
		\caption{Stretching factor $\kappa = 2.26$, redshift $z = 2.106$, off-axis angle $\chi = 5.41 \times 10^{-3}$.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{
		High and low energy light curves produced by the geometrical model. Burst parameter values are the same as discussed in section \ref{sec:parameters}.
	}
	\label{fig:sampleLightCurves}
\end{figure}

@@

\begin{figure}
	\hspace*{\fill}
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionHistogram}
		\label{fig:kappaDistributionHistogram}
		\caption{Histogram (blue) obtained from the model. Bar lines (black) show observed stretching factors.}
	\end{subfigure}
	\hfill
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[width=\textwidth]{kappaDistributionCDF}
		\label{fig:kappaDistributionCDF}
		\caption{CDF (blue) obtained from the model. Gray curve and bar lines show observed stretching factors.}
	\end{subfigure}
	\hspace*{\fill}
	\caption{Stretching factors histogram and CDF produced by our model. The sample contains $4096$ bursts.}
	\label{fig:kappaDistribution}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{correlations}
        \caption{Correlations between off-axis angles, stretching factors and high to low energy photon count ratios found in the sample produces by our model. The sample contains $4096$ bursts. Black crosses show observations. This correlation allows to estimate off-axis angles of observed bursts.}
        \label{fig:correlations}
\end{figure}
